\documentclass[12pt,a4paper,english]{article}
\usepackage{mathtools}
\usepackage{mathabx} 
\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[OT2,T1]{fontenc}
\usepackage{tcolorbox}
\usepackage[keeplastbox]{flushend}
\usepackage{color}
\usepackage{tikz-cd}
\usepackage{appendix}
\usepackage{babel}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage[bb=boondox]{mathalfa}
\geometry{top=3cm,bottom=3cm,left=2.5cm,right=2.5cm}
\setlength\parindent{0pt}
\renewcommand{\baselinestretch}{1.3}

\newcommand\restr[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}
  
% definition of the "structure"
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{coro}[thm]{Corollary}
\newtheorem{claim}{Claim}


\theoremstyle{definition}
\newtheorem{conj}{Conjecture}
\newtheorem{defi}{Definition}
\newtheorem*{example}{Example}
\newtheorem{exercise}{\textbf{\textcolor{red}{Exercise}}}
\newtheorem{step}{Step}

\theoremstyle{remark}

\newtheorem*{rem}{Remark}

% define new control sequence
\newcommand{\homo}{\mathbf{Hom}}
\newcommand{\Max}{\mathbf{Max}}
\newcommand{\spec}{\mathbf{Spec}}
\newcommand{\spm}{\mathbf{Spec}_{max}}
\newcommand{\Frac}{\mathbf{Frac}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\dif}{\text{d}}
\newcommand{\jac}{\textbf{Jac}}
\newcommand{\der}{\textbf{Der}}
\newcommand{\rank}{\text{rank}}
\newcommand{\sym}{\textbf{Sym}}
\title{Wely Law}
\date{\today}
\author{Deng Zhiyuan\footnote{Email:\ \href{mailto:dengzymathnt@outlook.com}{dengzymathnt@outlook.com}}}


\begin{document}
\maketitle
\newpage

\tableofcontents
\newpage

\section{Introduction}
The famous metaphor is hearing the drum. If someones hears some sound (spectral side) from the drum, Then one can calculate the volume (geometry side) of the drum.
    
    
    Wely proved
    \begin{equation}\label{weyl1}
        N(\lambda)=\frac{\textbf{Vol}(M)}{(4\pi)^{n/2}\Gamma(\frac{n}{2}+1)}\lambda^{n}+o(\lambda^{n}), \ \ \lambda\rightarrow\infty,
    \end{equation}
    in which $\Gamma$ is the Gamma functioin. And this formula
    can be taken an analog of  Rayleigh-Jeans law in physics: 

\begin{equation*}
    \rho(v,T)=\frac{8\pi v^{2}}{c^{3}}(kT)(1+ \text{O}(h)).
\end{equation*}

But this formula \ref{weyl1} doesn't have a finer structure of the eignvalue distribution. So we want a better estimation of the reminder term :
\begin{equation}\label{reminder}
   R(\lambda)=N(\lambda)-\frac{\textbf{Vol}(M)}{(4\pi)^{n/2}\Gamma(n/2+1)}.
\end{equation}

For a closed Riemann manifold, there is the optimal reminder term: $R(\lambda)=O(\lambda^{n-1})$.

For a bounded domain $\Omega\subset \mathbb{R}$, Weyl conjectured that there will be second term:

\begin{equation*}
    N(\lambda)=\frac{\textbf{Vol}(\Omega)}{6\pi^{2}\lambda^{3}}-\frac{\textbf{Vol}(\partial\Omega)}{16\pi}\lambda^{2}+o(\lambda^{2}).
\end{equation*}



    
While the non-compact case is more complicated with one more term:
    \begin{equation*}
      M(\lambda)=-\frac{1}{4\pi}\int^{\lambda}_{-\lambda}\frac{\phi'}{\phi}(\frac{1}{2}+ir)\dif r,
    \end{equation*}
    in which 
    \begin{equation*}
      \phi(s)=\frac{\zeta^{*}(2s-1)}{\zeta^{*}(2s)},\ \ \zeta^{*}(s)=\pi^{-\frac{s}{2}}\Gamma(\frac{s}{2})\zeta(s).
    \end{equation*}
    $\phi(s)$ is the determinant of scattering matrix and described by Eisenstein series.
        The project about automorphic Wely's law is the application of Selberg trace formula. 
    
    \begin{equation*}
    N(\lambda)+M(\lambda) \sim \frac{\text{Vol}(\Gamma\backslash \mathcal{H})}{4\pi}\lambda^{2},\ \ \ \lambda\rightarrow\infty    
    \end{equation*}
    
    
    This was first proved by Selberg. We are interested in $L^{2}_{cusp}$, and need to bound the contribution of $L^{2}_{cont}$ which is described by Eisenstein series. It can be done using the bound on Riemann zeta function.
\section{Wely law by Selberg trace formula}
\subsection{Recollection of Selberg trace formula}
\subsubsection{Recollection of Fundamental concepts: modular forms and algebraic number theory}
\begin{defi}

\end{defi}
\subsection{Proof of wely law by Selberg trace formula}
\section{Wely law with power saving error term by Finis-Lapid method}
\subsection{Recollection of trace of Hecke operator}
\subsubsection{Hecke operators}
\section{ON THE ASYMPTOTICS OF HECKE OPERATORS FOR REDUCTIVE
GROUPS}
\end{document}
